Preprocessing and exploration of the narwhal data for the analysis with smoothSDE

### 2024-06-02 R/preprocessing/data_preprocessing.Rmd
code updates

```{r}
#number of data points for each individual
for (id in unique(data$ID)) {
  narwhalDataBE=dataBE1[dataBE1$ID==id,]
  narwhalDataAE=dataAE[dataAE$ID==id,]
  cat(id," : ", length(narwhalDataBE$time)," GPS measurement before exposure and ", length(narwhalDataAE$time)," after exposure.\n",sep="")
}
```

>>>>

```{r}
#number of data points for each individual
for (id in unique(data$ID)) {
  narwhalDataBE=dataBE2[dataBE2$ID==id,]
  narwhalDataAE=dataAE[dataAE$ID==id,]
  cat(id," : ", length(narwhalDataBE$time)," GPS measurement before exposure and ", length(narwhalDataAE$time)," after exposure.\n",sep="")
}
```
